\systemEnding: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
edits to 2.2

A main drawback of an enumerative search algorithm is that we have no
efficient means of solving for arbitrary constants that might occur in the
program. In Sec.~\ref{regressionSection},
we will show how to find programs with real-valued constants
by automatically differentiating through the program and setting the constants using gradient descent.
%% In Sec.~\ref{textSection}
%% we will show that the bottom-up neural recognition model can learn
%% which discrete constants should be included in a program.

>>>>

A drawback of using an enumerative search algorithm is that we have no
efficient means of solving for arbitrary constants that might occur in the
program. In Sec.~\ref{regressionSection},
we will show how to find programs with real-valued constants
by automatically differentiating through the program and setting the constants using gradient descent.
%% In Sec.~\ref{textSection}
%% we will show that the bottom-up neural recognition model can learn
%% which discrete constants should be included in a program.
